Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-10-18 supp/index.Rmd
<edit index>

American Southeast, Caddo, archaeology, anthroinformatics, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, lithics, oblique parallel flaking

@@

  -   Bifaces _do not differ_ in shape, but **differ significantly** in size by raw material.
  -   Allometry (shape change with size) was not significant.
  -   Bifaces in the _large class_ recovered from Millsap Cache and Jowell Farm do not differ in shape or size, suggesting consistent morphology in bifaces from the _large class_, supporting arguments for production-based standardization.
  -   Bifaces in the _small class_ recovered from Millsap Cache and Jowell Farm **differ significantly** in size. Thus, while shape remains consistent, size differs, suggesting---at minimum---locally divergent approaches to retouch.
  -   Morphological disparity in the shape of the _small class_ is **significantly greater** at Jowell Farm, providing evidence for a more standardized approach to local retouch at Millsap Cache. This finding also provides support for the hypothesis that greater shape diversity is associated with retouch efforts, rather than production.

>>>>

American Southeast, Caddo, NAGPRA, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, ovoid biface, Jowell knife, Jowell knives, lithics, oblique parallel flaking

@@

  -   Bifaces _do not differ_ in shape, but **differ significantly** in size by raw material.
  -   Allometry (shape change with size) was not significant.
  -   Bifaces in the _large class_ recovered from Millsap Cache and Jowell Farm do not differ in shape or size, suggesting consistent morphology in bifaces from the _large class_, supporting arguments for production-based standardization.
  -   Bifaces in the _small class_ recovered from Millsap Cache and Jowell Farm **differ significantly** in size. Thus, while shape remains consistent, size differs, suggesting---at minimum---locally divergent approaches to retouch or retouch intensity.
  -   Morphological disparity in the shape of the _small class_ is **significantly greater** at Jowell Farm, providing evidence for a more standardized approach to local retouch at Millsap Cache. This finding provides additional support for the hypothesis that greater shape diversity is associated with retouch efforts, rather than production.
